### 2024-01-07 Paper/main.tex
Add description of codecs (#88)

To encode the loss less images into the respective codec for the experiment, several encoder where used.
\subsection{AVIF, JPEG and WebP}
For those encoders the python package pillow-avif-plugin and pillow was used. The additional pillow plugin can be installed via pip install pillow-avif-plugin. To encode a lossless image, the image is opened and save with a specific quality as seen in listing \ref{avif_1}. The quality parameter ranges from 1(lowest) to 100(highest). It is important to set the specific file extension for the software to
know in which codec the image needs to be encoded.
\begin{lstlisting}[label={avif_1}, language=Python, caption=Encode AVIF\, JPEG and WebP]
image = Image.open(image_path)
image.save(outputPath, quality=q)
\end{lstlisting}

\subsection{BPG}
To encode the images in BPG the Linux distribution from Fabrice Bellard's website (https://bellard.org/bpg/) was used. As seen in listing \ref{bpg_1} the output path is given after the -o argument and the specific quality after the -q argument. The quality parameter ranges from 51(lowest) to 0(highest). The last argument that needs no specific indicator is the original image.

@@

\subsection{HEIC}
Same as with the AVIF codec HEIC is also supported in a python package. For this codec the package pillow\_heif which can be installed with pip pillow-heif. The quality parameter ranges from 1(lowest) to 100(highest).
How the image can be encoded in HEIC is shown in listing \ref{heic_1}.

@@

\subsection{JPEG2000}
For the JPEG standards JPEG itself provides software to encode images. In the experiment the libopenjp2 was used. This library is in the Linux package manager and can be installed with apt-get install libopenjp2-tools. The quality parameter which ranges from 1(lowest) to 1000(highest) is given to the software with the -r parameter. An example how this can be done in Python is shown in listing \ref{jpeg2k_1}.
\begin{lstlisting}[label={jpeg2k_1}, language=Python, caption=Encode JPEG 2000]
subprocess.call('opj_compress -o ' + outputPath + \
                ' -r ' + str(int(maxQ - q)) + \
                ' -i ' + image_path,
                stdout=subprocess.DEVNULL,
                stderr=subprocess.DEVNULL,
                shell=True)
\end{lstlisting}

\subsection{JXL}
For JPEG XL the JPEG organization also provides a package which can be installed in Linux. For that encoder the libjxl (apt install libjxl-devtools) was used. The quality parameter ranges from 1(lowest) to 100 (highest) and an example to encode a image is shown in \ref{jxl_1}
\begin{lstlisting}[label={jxl_1}, language=Python, caption=Encode JPEG XL]
subprocess.call(['cjxl', image_path, outputPath,
                 '--quiet', '-q', str(q)])
\end{lstlisting}
\subsection{JXR}
For JXR the package libjxr-devtools was used. This includes a specific encoder and decoder app. The quality ranges from 0(lowest) to 1(highest). Here floating point numbers need to be used for quality.
An example how to encode a image with jxr is shown in \ref{jxr_1}. In addition to the quality parameter jxr also support quantization, although this results in very good compression rate, the image quality is affected drastically.
\begin{lstlisting}[label={jxr_1}, language=Python, caption=Encode BPG]
os.system('JxrEncApp -q ' + q_str + \
            ' -o ' + output_path + \
            ' -i ' + tif_path)
\end{lstlisting}

>>>>

To encode the loss less images into the respective codec for the experiment, several encoder where used.
\subsection{AVIF, JPEG and WebP}
\subsubsection{AVIF}
AVIF is a format that utilizes the AV1 video codec. The AV1 codec employs block-based predictive coding. In this method, the frame is broken down into smaller units. Those are then analyzed to predict repetitive motion and color data based on blocks that have been processed earlier. Once the prediction is made, the redundant data is removed from the block. 
To convert the image into a sum of cosine functions of different frequencies the Discrete Cosine Transform (DCT) is used.

\subsubsection{JPEG}
JPEG uses the Discrete Cosine Transform (DCT) to convert an image into a sum of cosine functions of different frequencies. After the DCT, the coefficients are quantized to reduce their precision, and then entropy coded to compress the resulting data. The entropy coding method used in JPEG is Huffman coding.

\subsubsection{WebP}
In WebP a similar compression mechanism to that of the VP8 codec is used. This involves segmenting the frame into smaller units. Each of those units motion and color information is predicted based on previously processed blocks. This prediction process allows for the removal of redundant data from each block. The remaining data is then transformed using the Discrete Cosine Transform (DCT).

For those encoders the python package pillow-avif-plugin and pillow was used. The additional pillow plugin can be installed via pip install pillow-avif-plugin. To encode a lossless image, the image is opened and save with a specific quality as seen in listing \ref{avif_1}. The quality parameter ranges from 1(lowest) to 100(highest). It is important to set the specific file extension for the software to
know in which codec the image needs to be encoded.
\begin{lstlisting}[label={avif_1}, language=Python, caption=Encode AVIF\, JPEG and WebP]
image = Image.open(image_path)
image.save(outputPath, quality=q)
\end{lstlisting}

\subsection{BPG}
The Better Portable Graphics (BPG) codec is a digital image coding file format, developed by Fabrice Bellard. It’s built upon the intra-frame encoding of the High Efficiency Video Coding (HEVC) video compression standard.

BPG operates on a block-by-block basis to transform image data into a form that minimizes redundancy. It employs high-quality decimation and interpolation (using 10 tap Lanczos filter and 7 tap Lanczos filter respectively) to manage chroma samples in 4:2:2 and 4:2:0 formats.

To encode the images in BPG the Linux distribution from Fabrice Bellard's website (https://bellard.org/bpg/) was used. As seen in listing \ref{bpg_1} the output path is given after the -o argument and the specific quality after the -q argument. The quality parameter ranges from 51(lowest) to 0(highest). The last argument that needs no specific indicator is the original image.

@@

\subsection{HEIC}
The High Efficiency Image File (HEIF) container, which uses the High Efficiency Video Coding (HEVC) compression standard, is the basis for the HEIC codec. This codec is used for storing both images and videos. 
The transformation is applied to pixel blocks, the size of which can range from 4x4 to 32x32. Depending on the type of block and the prediction mode, the transformation can be either a discrete cosine transform (DCT) or a discrete sine transform (DST).
Depending on the profile and level of the HEVC standard, the entropy coding can be either a context-adaptive binary arithmetic coding (CABAC) or a context-adaptive variable-length coding (CAVLC).

Same as with the AVIF codec HEIC is also supported in a python package. For this codec the package pillow\_heif which can be installed with pip pillow-heif. The quality parameter ranges from 1(lowest) to 100(highest).
How the image can be encoded in HEIC is shown in listing \ref{heic_1}.

@@

\subsection{JPEG2000}
In JPEG2000, the transformation process employs a discrete wavelet transform (DWT). The original image is divided into rectangular tiles that do not overlap. These tiles are then broken down into different levels of decomposition using DWT. Each level of decomposition contains a number of subbands, which are made up of coefficients that represent the characteristics of the original tile component’s horizontal and vertical spatial frequencies.
For entropy coding JPEG2000 uses Embedded Block Coding with Optimized Truncation (EBCOT). EBCOT is a context-based binary arithmetic encoder that consists of a Context Extractor (CE) and an Arithmetic Coder (AC).

For the JPEG standards JPEG itself provides software to encode images. In the experiment the libopenjp2 was used. This library is in the Linux package manager and can be installed with apt-get install libopenjp2-tools. The quality parameter which ranges from 1(lowest) to 1000(highest) is given to the software with the -r parameter. An example how this can be done in Python is shown in listing \ref{jpeg2k_1}.
\begin{lstlisting}[label={jpeg2k_1}, language=Python, caption=Encode JPEG 2000]
subprocess.call('opj_compress -o ' + outputPath + \
                ' -r ' + str(int(maxQ - q)) + \
                ' -i ' + image_path,
                stdout=subprocess.DEVNULL,
                stderr=subprocess.DEVNULL,
                shell=True)
\end{lstlisting}

\subsection{JXL}
JXL also uses the same basic technologies as JPEG2000, but with some improvements and innovations, such as learned lifting-based DWT and learned tree-based entropy coding.

For JPEG XL the JPEG organization also provides a package which can be installed in Linux. For that encoder the libjxl (apt install libjxl-devtools) was used. The quality parameter ranges from 1(lowest) to 100 (highest) and an example to encode a image is shown in \ref{jxl_1}
\begin{lstlisting}[label={jxl_1}, language=Python, caption=Encode JPEG XL]
subprocess.call(['cjxl', image_path, outputPath,
                 '--quiet', '-q', str(q)])
\end{lstlisting}
\subsection{JXR}
JXR uses a unique method that breaks down an image into smaller, individual rectangular tile areas. This is different from JPEG, which uses a single transformation stage. Instead, JXR applies its 4x4 core transform in a two-level hierarchical manner within 16x16 macroblock regions. This approach gives the transform a wavelet-like multi-resolution hierarchy, which enhances its compression capability.

When it comes to entropy coding, JXR’s process is more adaptable and intricate than JPEG’s. It includes a DC and AC coefficient prediction scheme, adaptive coefficient reordering (as opposed to JPEG’s fixed zigzag ordering), and a type of adaptive Huffman coding for the coefficients themselves. This entropy coding process enables efficient representation of the image data, which contributes to the overall compression performance.

Additionaly the Photo Overlap Transform (POT) is a key operation in JPEG XR encoding that reduces blocking artefacts and improves compression efficiency. There are three ways of setting the POT in JPEG XR, depending on the image format and the compression mode:

\textbf{No POT:} This is the simplest option, where no POT is applied to the image blocks. This is suitable for lossless compression or images with low bit depth (8 bits or less per channel).

\textbf{Half POT:} This option applies POT to half of the image blocks, alternating between odd and even rows and columns. This reduces the computation complexity and memory requirement of the POT, while still providing some benefits of overlap processing. This is suitable for lossy compression or images with medium bit depth (9 to 15 bits per channel).

\textbf{Full POT:} This option applies POT to all of the image blocks, creating a full overlap between adjacent blocks. This maximizes the quality and compression performance of the POT, but also increases the computation complexity and memory requirement. This is suitable for high-quality compression or images with high bit depth (16 bits or more per channel).

For JXR the package libjxr-devtools was used. This includes a specific encoder and decoder app. The quality ranges from 0(lowest) to 1(highest). Here floating point numbers need to be used for quality.
An example how to encode a image with jxr is shown in \ref{jxr_1}. In addition to the quality parameter jxr also support quantization, although this results in very good compression rate, the image quality is affected drastically.
\begin{lstlisting}[label={jxr_1}, language=Python, caption=Encode BPG]
os.system('JxrEncApp -q ' + q_str + \
            ' -o ' + output_path + \
            ' -i ' + tif_path)
\end{lstlisting}
